\input{command.tex}
\usepackage{parskip}

\newcommand{\applyteam}{Event Storage Platform}
\newcommand{\applycompany}{DataDog}
\newcommand{\applyrole}{Senior Software Engineer}

\begin{document}

\input{header.tex}

To whom it may concern,

I am writing to express my interest in applying to the \applyteam\ team at \applycompany\ as a \applyrole.
With over a decade as a full stack engineer, several years of backend focused work, and a track record for
mentoring and growing top talent, I believe I would be a valuable asset to not only the team, but the
organization as a whole.

During my years at BlueCross BlueShield of TN and HealthcareSource, I was instrumental as a full stack
engineer. With active involvment with the product teams, I was able to not only hone my technical skills,
but also learn how to balance engineering and business needs.

As my career progressed, I began to focus on the pure engineering challenges afforded
to backend development. I've excelled at leading and maintaining 3rd party integrations, full redesigns of
asynchronous job systems, and various other backend projects. The majority of my tenure at ThirtyMadison
involved working on foundation and core services teams where my work was entirely backend focused. In the
latter year, I became a leader of our Architecture Review Group.

With a specific note on DataDog, ThirtyMadison uses it extensively. I was not only a consumer of the data
we collected to establish dashboard, monitors, and metrics, but also enhanced our collection for analysis.
I spent several months developing and standardizing our background job metrics to better allow teams to
respond proactively to potential issues and reduce the risk of incidents.

At Vikus, I began on a 3 person team, but over the next several years, we grew it to 7.
Hiring two recent graduates, I thoroughly enjoyed mentoring and growing their technical skills. Being 
an active participant in another engineer's growth has and will continue to be a highlight in my career.

It is with excitement that I submit my application to \applycompany. I know my experience as a
full stack and backend engineer, and my skill as mentor sets me apart. Please see my attached resume and
letters of recommendation on LinkedIn for more details. Thank you for your consideration and I look forward
to meeting and discussing with you how best I could join and contribute to your organization.

\hfill \break
Sincerely,\\
\name

\end{document}