\documentclass[11pt,oneside]{article}
\usepackage{geometry}
\usepackage[T1]{fontenc}

\pagestyle{empty}
\geometry{letterpaper,tmargin=1in,bmargin=.8in,lmargin=1in,rmargin=1in,headheight=0in,headsep=0in,footskip=.3in}

\setlength{\parindent}{0in}
\setlength{\parskip}{0in}
\setlength{\itemsep}{0in}
\setlength{\topsep}{0in}
\setlength{\tabcolsep}{0in}

% Name and contact information
\newcommand{\name}{Eric Polino}
\newcommand{\addr}{814 Brynewood Park Lane, Chattanooga, TN 37415}
\newcommand{\phone}{(423) 618-6204}
\newcommand{\email}{aluink@gmail.com}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% New commands and environments

% This defines how the name looks
\newcommand{\bigname}[1]{
	\begin{center}\fontfamily{phv}\selectfont\Huge\scshape#1\end{center}
}

% A ressection is a main section (<H1>Section</H1>)
\newenvironment{ressection}[1]{
	\vspace{4pt}
	{\fontfamily{phv}\selectfont\Large#1}
	\begin{itemize}
	\vspace{3pt}
}{
	\end{itemize}
}

% A resitem is a simple list element in a ressection (first level)
\newcommand{\resitem}[1]{
	\vspace{-4pt}
	\item \begin{flushleft} #1 \end{flushleft}
}

% A ressubitem is a simple list element in anything but a ressection (second level)
\newcommand{\ressubitem}[1]{
	\vspace{-1pt}
	\item \begin{flushleft} #1 \end{flushleft}
}

% A resbigitem is a complex list element for stuff like jobs and education:
%  Arg 1: Name of company or university
%  Arg 2: Location
%  Arg 3: Title and/or date range
\newcommand{\resbigitem}[3]{
	\vspace{-5pt}
	\item
	{\textbf{#1}---#2 \hfill \textit{#3}}
}

% This is a list that comes with a resbigitem
\newenvironment{restitledposition}[3]{
	\resbigitem{#1}{#2}{#3}
	\vspace{-2pt}
	\begin{itemize}
}{
	\end{itemize}
}

% A resbigitem is a complex list element for stuff like jobs and education:
%  Arg 1: Name of company or university
%  Arg 2: Location
%  Arg 3: Title and/or date range
\newcommand{\resbigitemb}[2]{
	\vspace{-5pt}
	\item{\textbf{#1} \hfill \textit{#2}}
}

% This is a list that comes with a resbigitem
\newenvironment{resdateditem}[2]{
	\resbigitemb{#1}{#2}
	\vspace{-2pt}
	\begin{itemize}
}{
	\end{itemize}
}

% This is a simple sublist
\newenvironment{reslist}[1]{
	\resitem{\textbf{#1}}
	\vspace{-5pt}
	\begin{itemize}
}{
	\end{itemize}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Now for the actual document:

\begin{document}

\fontfamily{ppl} \selectfont

% Name with horizontal rule
\bigname{\name}

\vspace{-8pt} \rule{\textwidth}{1pt}

\vspace{-1pt} {\small\itshape \hfill \phone; \email \hfill}

\vspace{8 pt}

%%%%%%%%%%%%%%%%%%%%%%%% 
\begin{ressection}{Employment}

	\begin{restitledposition}{BlueCross BlueShield of TN (Chattanooga, TN)}{Analyst
Programmer}{July 2009--present}

    \ressubitem{\textbf{myBlueTN Mobile App:} Designed and built registration
    and user profile modules for a new hybrid mobile application. 
    Was the sole developer responsible for all future development, support, and 
    maintenance.}

		\ressubitem{\textbf{Inpatient Census Tool:} Designed and built a J2EE web 
    application to aggregate inpatient authorization data. Provided 
    multi-tier listings and incorporated predictive data to provide	better 
    foresight to the nursing staff.}
		
		\ressubitem{\textbf{Biometric Screening Interchange:} Designed and implemented
    data entry system along with a secure automated transfer mechanism to an
    offsite location using JSF and AES 256.}

		\ressubitem{\textbf{Breast Screening Survey:} Designed and implemented a call center application
		to survey members. Worked with reporting teams to report on the data.}

	\end{restitledposition}

	\begin{restitledposition}{Google Summer of Code (Mountain View, CA)}{Intern}{May 2009--Aug. 2009}

		\ressubitem{\textbf{GObjectification:} Worked on the \textit{Pidgin} open source project
		aiding in the conversion of the core instant message library to utilize the 
		GObject framework in C.}

		\ressubitem{\textbf{Hiding and Conversion:} Hid all existing data structures from scope.
		Converted existing structures to inherit from GObject, paradigm shifting the library's 
		architecture from procedural to object-oriented.}
		
		\ressubitem{\textbf{Abstract:} http://developer.pidgin.im/wiki/GSoC2009/HidingGobject}

	\end{restitledposition}

	\begin{restitledposition}{Campground Automation Systems (Mount Juliet, TN)}{Intern}{Jan. 2008--Apr. 2009}

    \ressubitem{\textbf{JAX-WS Development:} Developed a web service from scratch to
		manage campground automated reservation system utilizing Derby, PostgreSQL, 
		Cayenne, Hibernate, JAX-WS, Glassfish, and Maven.}
		
	\end{restitledposition}

	\begin{restitledposition}{Google Summer of Code (Mountain View, CA)}{Intern}{May 2007--Aug. 2007}

		\ressubitem{\textbf{Finch:} Developed enhancements to the open source console
		based instant message client \textit{Finch} in the \textit{Pidgin} project.}

		\ressubitem{\textbf{Sound:} Implemented sound, reusing most of the existing
		framework in order to limit an increase in codebase.}

		\ressubitem{\textbf{Logging:} Added the ability to log communications to file. 
		Provided a mechanism for searching previous conversations.}

		\ressubitem{\textbf{Remote Development:} Worked with developers across the globe in
		a decentralized remote development environment utilizing IRC, IM, and monotone.}

		\ressubitem{\textbf{Overview:} http://developer.pidgin.im/wiki/FinchFeat}
		
	\end{restitledposition}

	\begin{restitledposition}{Southern Adventist University (Collegedale, TN)}{Intern}{Aug. 2005--May 2006}

	\ressubitem{\textbf{Web Development:} Developed and maintained
	in-house portal system written in Java, JavaScript, HTML, and CSS.
	Utilized a custom RPC calling mechanism	to pull data asynchronously
	from servers utilizing Java and JavaScript.}

	\ressubitem{\textbf{Custom Time Clocks:} Soldered site-built time clocks to
	interface with the portal system.  Deployed the clocks across campus ensuring
	connectivity and functionality.}

	\end{restitledposition}

%	\begin{restitledposition}{TYCON Software (Red Deer, AB, Canada)}{Intern}{April 2005--July 2005}
%    \ressubitem{\textbf{Inventory Manager:} Aided in the design, development, and on-site deployment of 
%		custom VB.NET inventory management software to meet the needs of a large oil field equipment rental 
%		company.  Allowed for both on-screen management and updates via handheld Palm device.  Wrote Palm
%		software in .NET to interface with a barcode scanner.  Allowed for the device to dock and download to
%		a desktop machine where the desktop then parsed the data and updated the inventory system.}
%	\end{restitledposition}

%	\begin{restitledposition}{Delap SDA School (Delap, RMI)}{Teacher/System Administrator}{Aug. 2003--April 2005}
%    \ressubitem{\textbf{High school teacher:} Taught high school computer courses including typing, MS Office, networking,
%		programming, and PC troubleshooting.}
%		\ressubitem{\textbf{System Administrator:} Was the sole system administrator for a K-12 school in a third world country.
%		Managed dial-up connection sharing with WConnect.  Administered a mail server and all related hardware/software issues.
%	  Provided solutions to hardware and software issues on barebone machines when replacements weren't readily available.}
%	\end{restitledposition}

\end{ressection}

\begin{ressection}{Personal Projects}
  
  \begin{resdateditem}{Haskell Projects}{2010-Present}
    \ressubitem{Begun learning Haskell in 2010}
    \ressubitem{Currently working on a performance module for the Snap Web Framework}
  \end{resdateditem}


  \begin{resdateditem}{Suicide Chess}{2001-2004,2010-2011}
    \ressubitem{Wrote suicide chess program in C to play on the Free Internet Chess Server.}
    \ressubitem{Implemented the proof-number search algorithm for finding forced wins.}
    \ressubitem{Later rewrote in Java}
    \ressubitem{Utilized transposition tables and killer heuristics to reduce the branching factor of the $\alpha\beta$ search tree.}
  \end{resdateditem}

  \begin{resdateditem}{Reversi}{Fall 2008}
    \ressubitem{Wrote a Reversi engine in C for a tournament in college.}
%		\ressubitem{Implemented the proof-number search algorithm for finding forced wins.}
%		\ressubitem{Utilized transposition tables and killer heuristics to reduce the branching factor of the $\alpha\beta$ search tree.}
		\ressubitem{Created a genetic algorithm to improve the evaluation function.}
		\ressubitem{Won the tournament with a perfect record and the only engine to have a positive +/- score.}
  \end{resdateditem}
	
%	\begin{resdateditem}{Decaf Compiler}{Spring 2008}
%		\ressubitem{Designed and built a compiler to compile Decaf code into MIPS.}
%		\ressubitem{Built using Lex, Yacc, and C/C++}
%		\ressubitem{A variant of http://www.martinrinehart.com/project.html}
%	\end{resdateditem}

  \begin{resdateditem}{LOAPS POTM (http://dinsights.com/POTM/LOAPS/)}{2005}
    \ressubitem{Wrote a C program for the POTM programming contest that
    played LOAPS, a variant of the game Lines of Action.  It placed 8th
    with a 56-16-2 record.}
    \ressubitem{Used PN search to enhance play to find forced wins}
    \ressubitem{Created a genetic algorithm to learn an evaluation function.}
  \end{resdateditem}

\end{ressection}

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{Computer Experience}
  \resitem{Experience with Java, C, C++, HTML, CSS, JavaScript, Haskell, \LaTeX}
  \resitem{Comfortable in Windows and Unix/Linux environments.}
  \resitem{Wrote programs to play games such as Connect 4, Chess, Reversi, LOA, and Dots-and-boxes.}
\end{ressection}

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{Education}
	\begin{restitledposition}{Southern Adventist University (SAU)}{Cum Laude}{2005-2009}
		\resitem{B.S. Computer Science}
		\resitem{B.S. Mathematics}
	\end{restitledposition}
\end{ressection}


%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{Achievements and Activities}

	\resitem{Outstanding Computer Science Senior Award - SAU School of Computing}
	\resitem{President SAU Computer Club -- 2006-2007}
	\resitem{Cat 4 competitive road cyclist}
  \resitem{Fluently bilingual in French and English}

\end{ressection}


\end{document}
